A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-11-04 bioc-workflow.Rnw
mention processingData early on

@@

The ouput of running the \texttt{phenoDisco} algorithm is an
\texttt{MSnSet} containing the new data clusters, appended to the
\texttt{featureData} under the name \texttt{pd}. We can see by typing
\texttt{processingData(hl)} directly into the console the processing
information has been updated to the \texttt{MSnSet} recording the
parameters that were used to run the analyses.  This is handy for
keeping track of data analyses. The results can be displayed by using
the \texttt{getMarkers} function. We see that 5 new phenotype data
clusters were found.

>>>>

Another slot of interest is \texttt{processingData}, that logs the
processing \texttt{MSnSet} objects undergo. The processing log can be
accessed with the \texttt{processingData} function and is displayed
under \textit{Processing information} in the textual object summary
when an \texttt{MSnSet}'s name it typed in the R console.

@@

The ouput of running the \texttt{phenoDisco} algorithm is an
\texttt{MSnSet} containing the new data clusters, appended to the
\texttt{featureData} under the name \texttt{pd}. The results can be
displayed by using the \texttt{getMarkers} function. We see that 5 new
phenotype data clusters were found.
